Hardware-accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-04-21 paper.tex
Added subsections for different approaches
Better introduction to approaches section

\documentclass[12pt]{article}
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}

@@

Two different approaches.

% Boolean AND

@@

% Boolean XOR

>>>>

\documentclass{article}
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage{fancyvrb}

@@

We take two different approaches to rendering intersecting volumes using boolean
operations.  The boolean operations involved are AND and XOR.  AND takes the
intersection of two shapes, while XOR, meaning exclusive OR, takes everything
but the intersection.

\subsection{Boolean AND with Depth Buffer Masking}

@@

\subsection{Boolean AND with Boolean XOR}
